% !TeX TS-program = pdflatex
% !BIB TS-program = bibtex
\documentclass{article}
\input{config}
\input{meta}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\maketitle
\tableofcontents
\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{General Information}
% ==============================================================================
\subsection{Identifying Information}
\paragraph{Date} 2020 February
\paragraph{Principle Investigators \& Affiliations}\n
Jesse Knight\aff{1};
Sharmistha Mishra\aff{1}
\par
\aff{1}Institute of Medical Sciences, University of Toronto
\paragraph{Co-Investigators}
N/A
\paragraph{Review Title}\n
\textit{\reviewtitle}
\paragraph{Research Funding}
NSERC CGS-D
% ==============================================================================
\subsection{Background \& Rationale}
\input{rationale}
\clearpage % TEMP
% ==============================================================================
\subsection{Review Questions}
\label{ss:questions}
\input{research-qs}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Methods}
\label{s:methods}
% ==============================================================================
\subsection{Eligibility Criteria}
\label{ss:eligibility}
We have different scopes for each of our research questions as follows:
\begin{enumerate}[itemsep=0pt]
  \item any type of transmission model, in \ssa context
  \item deterministic compartmental transmission models, in any context
  \item deterministic compartmental transmission models, in \ssa context
\end{enumerate}
Most of our eligibility criteria apply for all 3 questions,
but regarding these three scopes, let:
\ss{c} = criteria for deterministic compartmental transmission models, and
\ss{s} = criteria for \ssa context.
%\footnote{We define \ssa as the following countries: \input{ssa.names}.}
Our criteria are:
% ------------------------------------------------------------------------------
\paragraph{Publication Details}\n
\begin{criteria}{Include}
  \item English language
  \item published before 2020
  \item peer-reviewed journal article (not review)
\end{criteria}
\begin{criteria}{Exclude}
  \item non-English language
  \item published in 2020 or later
  \item non-peer reviewed journal article
  \item review article (references will be screened)
  \item textbook, grey literature, opinions, comments, conference abstracts
\end{criteria}
% ------------------------------------------------------------------------------
\paragraph{Mathematical Model of Transmission}\n
\begin{criteria}{Include}
  \item dynamical model
  \item between-host dynamics
  \item deterministic model\ss{c}
  \item compartmental model\ss{c}
\end{criteria}
\begin{criteria}{Exclude}
  \item no mathematical modelling
  \item non-dynamical model
  \item within-host/cellular/protein modelling
  \item mouse models
  \item stochastic (random) model\ss{c}
  \item individual-based model\ss{c}
\end{criteria}
% ------------------------------------------------------------------------------
\paragraph{Epidemic Context}\n
\begin{criteria}{Include}
  \item \hiv modelled (at least)
  \item any region in Sub-Saharan Africa (\ssa)\ss{s}
\end{criteria}
\begin{criteria}{Exclude}
  \item only other infections modelled
  \item theoretical context or only region(s) outside of \ssa modelled\ss{s}  
\end{criteria}
\clearpage % TEMP
% ==============================================================================
\subsection{Information Sources}
We search the following databases: \textsc{medline}, \textsc{embase} via Ovid.
% ==============================================================================
\subsection{Search Strategy}
Our search strategy aims to identify
any type of \hiv transmission model applied in any context.
We will later manually identify
which models were deterministic and compartmental,
and which works applied the model to \ssa context.
% ------------------------------------------------------------------------------
\paragraph{Validation References}\n
Before performing the search, we identified
9 publications of \hiv modelling applied to \ssa,
and 9 publications of \hiv modelling applied elsewhere.
We ensure that these 9+9 validation references (VR)
are contained in our search results,
as an indicator that the search is performing well.
\par
\valrefs{\ssa}{validation/ssa.bibid}
\valrefs{other contexts}{validation/extra.bibid}
% ------------------------------------------------------------------------------
\paragraph{Search Terms}\n
We operationalize our inclusion \& exclusion criteria
using the following search terms, where \lstinline|term/| denotes a MeSH term,
\lstinline|tw| searches all text fields, and
\lstinline|kf| searches all heading fields.
We implement publication year and language criteria via Ovid ``limits'',
but did not filter publication types (review, etc.),
as we found such classifications to be unreliable.
Additionally, we exclude the MeSH term \lstinline|animal/|.
\begin{center}
  % search terms in search/ folder
  \begin{tabular}{rp{0.75\linewidth}}
  	\toprule
  	Criteria & Search Terms        \\
  	\midrule
  	    \hiv & \getsearch{hiv}     \\
  	\midrule
  	   model & \getsearch{model}   \\
  	\midrule
  	 exclude & \getsearch{exclude} \\
  	\midrule
  	  limits & \getsearch{limits}  \\
  	\bottomrule
  \end{tabular}
\end{center}
% ------------------------------------------------------------------------------
\paragraph{Results}\n
The results from \textsc{medline} \& \textsc{embase} on 2020 March 15 were:
\begin{center}
\begin{tabular}{crrp{0.75\linewidth}}
	\toprule
	  &    Total Hits &  VR & Terms                              \\
	\midrule
	1 &  \num{773236} & 9+9 & \getsearch{hiv}                    \\
	\midrule
	2 & \num{1294099} & 9+9 & \getsearch{model}                  \\
	\midrule
	3 & \num{8519337} & 0+0 & \getsearch{exclude}                \\
	\midrule
	4 &   \num{15133} & 9+9 & \lstinline|1 AND 2|                \\
	\midrule
	5 &   \num{13948} & 9+9 & \lstinline|1 AND 2 NOT 3|          \\
	\midrule
	6 &   \num{13553} & 9+9 & \lstinline|1 AND 2 NOT 3 (limits)| \\
	\bottomrule
\end{tabular}
\end{center}
where VR = validation references hit.
These results (6) then form our initial database for screening.
% ==============================================================================
\subsection{Data Management}
Based on the initial search,
the bibliographic information (including abstract)
of non-duplicate matching items will be
exported from the search result in \textsc{xml} format,
and uploaded to Covidence for abstract screening.
Covidence provides tools for including and excluding items
based on a set of user-defined criteria,
tracking the results of review.
\par
The full texts of included items will then be sought
using institutional access and support.
For each item, the data extraction form given in Appendix~\ref{app:form}
(Google Forms) will be completed.
Upon submission of the form, a row in the linked tabular database
(Google Sheets) will be automatically populated with the results.
Analysis of the tabular data will then be performed in Python,
with the aim of generating statistics and figures to answer
the \nameref{ss:questions}.
% ==============================================================================
\subsection{Selection Process}
Following upload of the initial search results to Covidence,
one reviewer (JK) will screen the abstracts for inclusion
using the \nameref{ss:eligibility}.
Unclear edge cases will be resolved by discussion with SM.
% ==============================================================================
\subsection{Data Extraction}
Appendix~\ref{app:form} gives the data extraction form to be used
for each included reference.
The form includes a combination of
short text inputs and pre-defined categorical variables
in the following sections:
\newcommand{\ibox}[1]{\parbox{0.25\linewidth}{#1}}
\begin{itemize}
	\item \ibox{Article meta-data:}     authors, journal, title, etc.
	\item \ibox{Model context:}         geography, time, research questions
	\item \ibox{Model approach:}        model type, code
	\item \ibox{Modelled populations:}  sex, age, risk, turnover, interventions
	\item \ibox{Modelled biology:}      \cdf, viral load, treatment
	\item \ibox{Modelled transmission:} modes, types of acts, partnership types, modifiers
	\item \ibox{Data:}                  calibration targets
\end{itemize}
Some short text inputs will capture semi-structured data,
such as the relative sizes of population strata, like:
\par
  \lstinline|HSF-low: 0.35, HSF-medium: 0.125, HSF-high: 0.025, ...|
\par
corresponding to: heterosexual females in the low risk group representing
$0.35$ proportion of the total population, etc.
Provided the input are structured in the suggested way,
the text can later be parsed in Python,
even though the population strata definitions may change from model to model.
\par
Data extraction and subsequent analysis will be completed by one reviewer (JK).
% ==============================================================================
\subsection{Quality Assessment}
N/A
% ==============================================================================
\subsection{Data Synthesis [TBD]}
% ------------------------------------------------------------------------------
\subsubsection{Question \ref{q:context}: Context}
% ------------------------------------------------------------------------------
\subsubsection{Question \ref{q:hetero}: Parameterizations}
% ------------------------------------------------------------------------------
\subsubsection{Question \ref{q:trends}: Trends}
\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\printbibliography
\clearpage
\appendix
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\includepdf[pages=1,pagecommand={\section{Data Extraction Form}\label{app:form}}]
%{../data/extraction-form.pdf}
%\includepdf[pages=2-,pagecommand={}]
%{../data/extraction-form.pdf}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
