\title{Risk heterogeneity in compartmental HIV transmission models of ART as prevention in Sub-Saharan Africa: A scoping review}
\runhead{Heterogeneity in transmission models}
\author[1,a,*]{Jesse~Knight}
\author[2,b]{Rupert~Kaul}
\author[1,3,4,5,c]{Sharmistha~Mishra}
\affil[1]{Institute of Medical Science, University of Toronto, Toronto, Canada}
\affil[2]{Department of Medicine, University of Toronto, Toronto, Canada}
\affil[3]{MAP Centre for Urban Health Solutions, Unity Health Toronto, Toronto, Canada}
\affil[4]{Division of Infectious Disease, Department of Medicine, University of Toronto, Toronto, Canada}
\affil[5]{Institute of Health Policy, Management and Evaluation,
  Dalla Lana School of Public Health, University of Toronto, Toronto, Canada}
\affil[a]{ORCID: 0000-0002-0455-5455}
\affil[b]{ORCID: 0000-0002-1586-4093}
\affil[c]{ORCID: 0000-0001-8492-5470}
\affil[*]{Corresponding Author: Jesse Knight.
  Desk 326.2, MAP Centre for Urban Health Solutions.
  30 Bond St, Toronto ON, M5B 1W8.
  jesse.knight@mail.utoronto.ca}
\date{May 25, 2021}
\words{240}{3500}
\keywords{%
  HIV,
  Mathematical Model,
  Computer Simulation,
  Antiretroviral Therapy,
  Population Heterogeneity,
  Risk Factors,
  Healthcare Disparities
}
\coi{\input{coi.txt}}
\funding{%
  The study was supported by
  the Natural Sciences and Engineering Research Council of Canada (NSERC CGS-D);
  Ontario Early Researcher Award No.~ER17-13-043; and
  the Canadian Institutes of Health Research Foundation Grant (FN-13455).
}
\acknowl{%
  We thank:
  Kristy Yiu (Unity Health Toronto) for research coordination support;
  Linwei Wang (Unity Health Toronto) for feedback on elements of the paper; and
  Kaitlin Fuller (University of Toronto) for her help designing the search strategy.
}
\contrib{%
  JK and SM conceptualized and designed the study, and developed the search strategy.
  JK performed the search, extracted the data, conducted the analysis, and generated the results.
  JK and SM drafted the manuscript and appendix.
  All authors (JK, RK, and SM) reviewed the results and contributed to writing the manuscript.
}
